---
title: "Reading Data"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)


theme_set(theme_minimal()+theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colur = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Scrape a table 

I want the first table from [this page](http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm)


Read in the html. 

```{r}
url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_html = read_html(url)
```


Extract the tables; focus on the first one

```{r}
tabl_marj = 
  drug_use_html %>% 
  html_nodes(css = "table") %>% 
  first() %>% 
  html_table() %>% 
  slice(-1) %>% 
  as_tibble()
```


## Star Wars Movie info

I want the data from [here](https://www.imdb.com/list/ls070150896/)

```{r}
url = "https://www.imdb.com/list/ls070150896/"

swm_html = read_html(url)
```

Grab elements that I want. 

```{r}
title_vec = 
  swm_html %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()

gross_rev_vec = 
  swm_html %>%
  html_nodes(".text-small:nth-child(7) span:nth-child(5)") %>%
  html_text()

runtime_vec = 
  swm_html %>% 
  html_nodes(".runtime") %>% 
  html_text()

swm_df = 
  tibble(
    title = title_vec, 
    gross_rev = gross_rev_vec, 
    runtime = runtime_vec
  )
```


## Get some water data 

Reading in from APIs, which is good for data that is updated

```{r}
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% 
  content("parsed")


nyc_water_json = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>% 
  jsonlite::fromJSON() %>% 
  as_tibble()
```

##BRFSS
Same process, different data 

```{r}
brfss_smart2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000)) %>% 
  content("parsed")
```


## Some data is not so nice...

Let's look at Pokemon

```{r}
pokemon_data = GET("http://pokeapi.co/api/v2/pokemon/1") %>%
  content()

pokemon_data$name
pokemon_data$height
pokemon_data$abilities
```

## Closing thoughts 

Be reasonable in the requests because every time you knit or run the code you are sending requests to server. Can be spammy and slow down. 





